---
title: "Benford_Project"
author: "Summer Zu, Tianying Xi, Vector Liu, Sky Liu"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(
  "ggplot2",
  "knitr",
  "readxl",
  "readr",
  "tidyr",
  "dplyr",
  "zoo",
  "esquisse",
  "matlab",
  "lattice",
  "grid",
  "gridExtra",
  "arm",
  "ggpubr",
  "benford.analysis",
  "data.table"
)
```

```{r}


data = fread("fec-independent-expenditures.csv")
data1<-data%>%dplyr::select(committee_id,committee_name,report_year,payee_name,payee_state,expenditure_description,expenditure_date,expenditure_amount,office_total_ytd,support_oppose_indicator,candidate_id,candidate_name,candidate_office,transaction_id)
#whether the ads is in support of or opposition to the candidate
support<-data%>%filter(support_oppose_indicator=="S")
oppose<-data%>%filter(support_oppose_indicator=="O")
#candidate office: P(president), S(senate), H(house)
president<-data%>%filter(candidate_office=="P")
senate<-data%>%filter(candidate_office=="S")
house<-data%>%filter(candidate_office=="H")
```


##Benford analysis on all advertising expenditure
```{r}
bfd_cp <- benford(data1$expenditure_amount)
plot(bfd_cp)
bfd_cp

```

##Further analysis on suspected expenditures

52251 suspected expenditure out of 413237
21202 happened in 2012 and 27767 in 2016, election year
25833 were for president election, 23715 were for senate election
About half of the suspected expenditure were in support of the candidate (27844) and the other half were in opposition to the candidate (24402)

The top candidate with the largest amount of suspected expenditure in support of the candidate is HILLARY CLINTON (7386).
The top candidate with the largest amount of suspected expenditure in opposition to the candidate is DONALD TRUMP (7386).

```{r}
suspects_cp <- getSuspects(bfd_cp, data1)

#most of suspect expenditures happens in 2012 and 2016
table(suspects_cp$report_year)
#most of suspect expenditures happens in president and senate election
table(suspects_cp$candidate_office)
table(suspects_cp$support_oppose_indicator)
s_suspects <- suspects_cp%>%filter(support_oppose_indicator=="S")
o_suspects <- suspects_cp%>%filter(support_oppose_indicator=="O")
s_sus_candidate<-as.data.frame(table(s_suspects$candidate_name))
s_sus_candidate<-s_sus_candidate%>%arrange(Freq)
top_s_sus_candidate<-tail(s_sus_candidate)

o_sus_candidate<-as.data.frame(table(o_suspects$candidate_name))
o_sus_candidate<-o_sus_candidate%>%arrange(Freq)
top_o_sus_candidate<-tail(o_sus_candidate)

```

##Benford Analysis on Trump Expenditure

The majority of suspected expenditure in opposition to Trump were from WORKING AMERICA.
```{r}
TRUMP<-data1%>%filter(candidate_name=="TRUMP, DONALD")
bfd_Trump <- benford(TRUMP$expenditure_amount)
plot(bfd_Trump)
bfd_Trump

suspects_Trump <- getSuspects(bfd_Trump, TRUMP)
table(suspects_Trump$committee_name)
```
##Benford Analysis on Trump Expenditure

The majority of suspected expenditure in support of Clinton were from WORKING AMERICA.
```{r}
Clinton<-data1%>%filter(candidate_name=="CLINTON, HILLARY")
bfd_Clinton <- benford(Clinton$expenditure_amount)
plot(bfd_Clinton)
bfd_Clinton

suspects_Clinton <- getSuspects(bfd_Clinton, Clinton)
table(suspects_Clinton$committee_name)
```